Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-07-11 manuscript/manuscript.Rmd
Adding author attributions to manuscript directly
Using hacky footnote version but I think it looks ok?

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author: "William Kumler, Wei Qin, Rachel A. Lundeen, Benedetto Barone, Laura T. Carlson, and Anitra E. Ingalls"
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---

>>>>

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler^[School of Oceanography, University of Washington, Seattle, WA, USA], Wei Qin^[School of Biological Sciences, Institute for Environmental Genomics, University of Oklahoma, Norman, OK, USA], Rachel A. Lundeen$^1$, Benedetto Barone^[Daniel K. Inouye Center for Microbial Oceanography, Research and Education and Department of Oceanography, University of Hawai'i at Mānoa, Honolulu, HI, USA], Laura T. Carlson$^1$, Anitra E. Ingalls$^{1*}$ (aingalls@uw.edu)
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---
